---
title: "Replication"
author: "Dan Zhang"
date: "2024-03-31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Remove all objects from the workspace
rm(list = ls())
# LOAD PACKAGES
library(readr)   # readr_1.0.0: READ IN DATA WITH 'read_tsv()'
library(dplyr)   # dplyr_0.5.0: HELPER FUNCTIONS, e.g., '%>%'
library(texreg)  # texreg_1.36.7: PRINT SUMMARIES OF DATA WITH 'screenreg()'

library(MASS) # For VIF
library(car)  # Diagnostic plot for Logit model
library(ResourceSelection) # For Hosmer-Lemeshow test
# Set currency working directory
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

## Load data
```{r}
alexandria_data <- read_tsv("Alexandria_Data.tsv")
```

## Variables
Explanatory variables
- Control variables
- z1ev: an individual’s weighted eigenvector network centrality
- z1elite_avgprox: measure of elite proximity

Outcome variables
- turnout: binary variable indicating whether an individual voted

## Identify control variables
```{r}
alexandria_controls_with_nl <- c(
  "hhwealth",    # Household wealth (thousands of dollars)" , continous
  "hhwealthlog", # ln(Household wealth) , continous
  "midstatus",   # Mid-status occupation , categorical 0/1
  "highstatus",  # High-status occupation, categorical 0/1
  "owner",       # Owns home? , categorical 0/1
  "age",         # Age (years) , continous
  "agelog",      # ln(Age) , continous
  "church",      # Is church member? , categorical 0/1
  "usborn"       # Is U.S. born? , categorical 0/1
) %>%
  paste(collapse = " + ")
```

## Run turnout models (Table 1)--Original results
```{r}
# MODEL 1
# Basline model:only personal attributes as explanatory variables.
alexandria_turnout_1 <- paste("turnout ~ ",
                              alexandria_controls_with_nl)  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_1)

# MODEL 2
# Add z1ev: an individual’s weighted eigenvector network centrality
alexandria_turnout_2 <- paste("turnout ~ ",
                              alexandria_controls_with_nl,
                              "+ z1ev")  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_2)

# MODEL 3
# Add z1ev:an individual’s weighted eigenvector network centrality
# and z1elite_avgprox: measure of elite proximity.
alexandria_turnout_3 <- paste("turnout ~ ",
                              alexandria_controls_with_nl,
                              "+ z1ev + z1elite_avgprox")  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_3)
```

```{r}
# Perform sensitivity test, make sure adding network variables is significant
# These relationships are powerful in confounding the clustering of interests and environmental impacts within the network.
anova(alexandria_turnout_1, alexandria_turnout_3, test = "Chisq")
```

## Check assumptions of glm-logistic regression
```{r}
# Residual analysis and outlier detection
par(mfrow = c(2, 2))
plot(alexandria_turnout_3)
```

```{r}
# Model goodness of fit test
hoslem.test(alexandria_turnout_1$y, fitted(alexandria_turnout_1), g=10)
hoslem.test(alexandria_turnout_2$y, fitted(alexandria_turnout_2), g=10)
hoslem.test(alexandria_turnout_3$y, fitted(alexandria_turnout_3), g=10)

# Check for multicollinearity
vif(alexandria_turnout_3)
```
Good model fit and multicollinearity issue between age and agelog. The multicollinearity issue might because of the data distribution of age. 

## Add ordered satus variable
```{r}
# Create 'statuslevel' based on 'midstatus' and 'highstatus'
alexandria_data$statuslevel <- ifelse(alexandria_data$midstatus == 1, "middle status", 
                           ifelse(alexandria_data$highstatus == 1, "high status", "non-status"))
  
# Convert 'statuslevel' to an ordered factor
alexandria_data$statuslevel <- factor(alexandria_data$statuslevel, levels = c("non-status", "middle status", "high status"), ordered = TRUE)

```
## Add ordered satus variable
```{r}
new_controls <- c(
  "hhwealth",    # Household wealth (thousands of dollars)" , continous
  "hhwealthlog", # ln(Household wealth) , continous
  "statuslevel", # Mid-status occupation , categorical 0/1
  "owner",       # Owns home? , categorical 0/1
  "age",         # Age (years) , continous
  "agelog",      # ln(Age) , continous
  "church",      # Is church member? , categorical 0/1
  "usborn"       # Is U.S. born? , categorical 0/1
) %>%
  paste(collapse = " + ")

# TABLE 1, MODEL 7
alexandria_turnout_7 <- paste("turnout ~ ",
                              new_controls)  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_7)


# TABLE 2, MODEL 8
alexandria_turnout_8 <- paste("turnout ~ ",
                              new_controls,
                              "+ z1ev")  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_8)

# TABLE 2, MODEL 9
alexandria_turnout_9 <- paste("turnout ~ ",
                              new_controls,
                              "+ z1ev + z1elite_avgprox")  %>%
  formula()  %>%
  glm(data = alexandria_data,
      family = binomial(link = "logit"))
summary(alexandria_turnout_9)
```

## Display results
```{r}
# # Table 1
# list(
#   alexandria_turnout_1,
#   alexandria_turnout_2,
#   alexandria_turnout_3,
#   alexandria_turnout_4,
#   alexandria_turnout_5,
#   alexandria_turnout_6
# )  %>%
#   screenreg(digits = 3,
#             stars = .05)

# Table 2
list(
  alexandria_turnout_1,
  alexandria_turnout_2,
  alexandria_turnout_3,
  alexandria_turnout_7,
  alexandria_turnout_8,
  alexandria_turnout_9
)  %>%
  screenreg(digits = 3,
            stars = .05)
```


```{r}
# Model goodness of fit test
# hoslem.test(alexandria_turnout_4$y, fitted(alexandria_turnout_4), g=10)
# hoslem.test(alexandria_turnout_5$y, fitted(alexandria_turnout_5), g=10)
# hoslem.test(alexandria_turnout_6$y, fitted(alexandria_turnout_6), g=10)
hoslem.test(alexandria_turnout_7$y, fitted(alexandria_turnout_7), g=10)
hoslem.test(alexandria_turnout_8$y, fitted(alexandria_turnout_8), g=10)
hoslem.test(alexandria_turnout_9$y, fitted(alexandria_turnout_9), g=10)
```
```{r}
anova(alexandria_turnout_3, alexandria_turnout_9, test = "Chisq")
```

```{r}

